Global Climate of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-10-28 ms.tex
model comparison

We calculated the planet-to-star flux $F_p/F_s$ in two different ways. First, we fit a sinusoid with a period equal to the planet's orbital period. The free parameters were the sine curve amplitude and phase offset. For the second approach, we used the \texttt{SPIDERMAN} package \citep{louden17} to model $F_p/F_s$. This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding flux ratio for an observation at time $t$. In our fit, we calculated the stellar flux with a PHOENIX model \citep{husser13} interpolated to an effective temperature of $6110\,\mathrm{K}$ \citep{gillon14}.  For the planet flux, we tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang16}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).

@@

\subsection{Comparison of Thermal Phase Variation Models}
All four of the thermal phase variation models we consider (two-temperature, kinematic, spherical harmonics, and sinusoid) provide good fits to the observed phase curves. Table FIXME summarized the goodness of fit

These models each have different strengths: the kinematic model incorporates the most prior knowledge of physics, and even though it makes several simplifying assumptions (e.g, that the wind speed and direction are constant), it closely reproduces GCM simulations over a wide parameter space \citep{zhang16}.   The spherical harmonics map is the most flexible and makes the fewest assumptions about the true climate. The two-temperature model is the simplest and easiest to compare to one-dimensional models of the dayside, which assume a uniform temperature/pressure profile.  In all cases, we assumed that the planet is tidally locked, such that each orbital revolution corresponds to one complete rotation on its spin axis. %In addition to these maps, we also fit the phase variation with a sinusoid, which has been used for many past analyses of exoplanet phase curves (FIXME).

>>>>

We calculated the planet-to-star flux $F_p/F_s$ in two different ways. First, we fit a sinusoid with a period equal to the planet's orbital period. The free parameters were the sine curve amplitude and phase offset. For the second approach, we used the \texttt{SPIDERMAN} package \citep{louden17} to model $F_p/F_s$. This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding flux ratio for an observation at time $t$. In our fit, we calculated the stellar flux with a PHOENIX model \citep{husser13} interpolated to an effective temperature of $6110\,\mathrm{K}$ \citep{gillon14}.  For the planet flux, we tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang16}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).  In all cases, we assumed that the planet is tidally locked, such that each orbital revolution corresponds to one complete rotation on its spin axis.

@@

\subsection{Comparison of Thermal Phase Variation Models}
We compared four different models for the thermal phase variation: a sinusoid and three temperature maps. The sinusoid has been the most widely used model for thermal phase variation in previous analyses of thermal phase curves \citep{FIXME} and directly fits the phase variation amplitude and offset from the substellar point. Fitting temperature maps (two-temperature, kinematic, and spherical harmonics) is a new approach enabled by the \texttt{SPIDERMAN} package.  The three maps each have different strengths: the kinematic model incorporates the most prior knowledge of physics, and even though it makes several simplifying assumptions (e.g, that the wind speed and direction are constant), it closely reproduces GCM simulations over a wide parameter space \citep{zhang16}.   The spherical harmonics map is the most flexible and makes the fewest assumptions about the true climate. The two-temperature model is the simplest and easiest to compare to one-dimensional models of the dayside, which assume a uniform temperature/pressure profile.

All of the models provide good fits to the observed phase curves. Table\,\ref{tab:model_comparison} summarized the goodness of fit according to the reduced $\chi^2$, Bayesian information criterion (BIC), and Aikike information criterion (AIC). These metrics for assessing fit quality are . The AIC penalizes model complexity relatively LESS? than the BIC. 
Spherical harmonics provide the best fit most of the time.

The kinematic model overpredicts the nightside flux. Model is not very flexible because nightside flux is assumed to be constant.
The two temperature model overpredicts the flux at quadrature and underpredicts the dayside.

What is the difference in min/max temperature?
